Trifunctional Phosphatidylethanolamine

### 2025-03-25 LipidProbe/FormattingTemplate.qmd
adding credit to Berit for the structures
example

---
title: "Formatting Template"
subtitle: "HTML page of individual lipid probe data"
---

@@

# # Building an ID column to maintain the order on the x-axis
# ID <- c()
# for(i in 0:(nrow(data))){
# 	ID[i] = i
# }

# # Applies the ID column to the Spa results
# data_ranked <- data |>
#     arrange(logFC) |>
# 	filter(LipidProbe == "1-10 FA") |>
# 	mutate(ID = ID)

>>>>

---
title: "Formatting Template"
subtitle: "HTML page of individual lipid probe data"
format: 
  html:
    embed-resources: false
---

@@

### 2025-03-25 LipidProbe/PhosphatidicAcid.qmd
adding a draft of the NAPE page
putting NAPE on the index
example

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
format:
  html: default
callout-icon: false
---

@@

data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))

@@

## Gene Ontology Analysis

@@

#### Cell Compartment

@@

#### Molecular Function

@@

#### Biological Process

@@

## Data exploration and download

>>>>

---
title: "Trifunctional Phosphatidic Acid"
prefer-html: true
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))

@@

#### Gene Ontology Analysis

@@

##### Cell Compartment

@@

##### Molecular Function

@@

##### Biological Process

@@

#### Data exploration and download

### 2025-03-25 LipidProbe/Phosphatidylethanolamine.qmd
putting NAPE on the index
example

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
format:
  html: default
callout-icon: false

---

@@

:::{.border}
![Trifunctional Phosphatidylethanolamine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PE.png)
:::

>>>>

---
title: "Trifunctional Phosphatidylethanolamine"
prefer-html: true
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@
